% % Use the command with details
\experienceSubsection
    {Data Scientist}
    {Mirafra}
    {Sep 2024 -- Present}
    {%
        \item Developed an automated testing framework for ONNX models tailored to the AMD AI Engine, streamlining model validation and enhancing the engine’s performance and reliability.
    }


\experienceSubsection
    {Deputy Manager – Software Developer}
    {Jio}
    {Jan 2022 -- Sep 2024}
    {%
        \item Spearheaded the design and deployment of an AI Noise Suppression system in collaboration with Nvidia, significantly enhancing audio quality for JioMatrix.
        \item Developed a robust media engine for the JioMeet platform using Google WebRTC, enabling seamless cross-platform communication on Linux and Android.
        \item Automated the CI/CD pipeline for server deployments, achieving an 80\% efficiency boost and reducing human errors.
        \item Built a custom load-balancing library for all microservices and implemented monitoring solutions using Zookeeper and Grafana, ensuring high performance and reliability.
        \item Designed and developed a SIP gateway for JioMeet Enterprise, enabling compatibility with multiple video conferencing clients.
    }

\experienceSubsection
    {Associate Software Engineer – Product Development}
    {HARMAN International}
    {Dec 2020 -- Dec 2021}
    {%
        \item Designed and developed a desktop simulator for an IoT device, streamlining the development process and doubling overall efficiency.
        \item Engineered real-time data visualization for an embedded healthcare device without GPU acceleration, maintaining CPU usage below 30\%.
        \item Created a dynamic front-end for a vaccination booking portal in just one month, enabling employees across the country to schedule vaccine appointments seamlessly.
        \item Built an emulator to simplify the development process, achieving a 25\% boost in team efficiency.
    }

\experienceSubsection
    {Associate Professional Software Engineer}
    {DXC Technology}
    {Jul 2020 -- Nov 2020}
    {%
        \item Excelled as a Salesforce developer with outstanding performance on Trailhead, designing and implementing an analytics dashboard layout using Salesforce Einstein.
    }

\experienceSubsection
    {Research Intern}
    {Indian Space Research Organisation}
    {Jun 2019 -- Sep 2019}
    {%
        \item Conducted research on semantic segmentation of satellite images using deep learning models, processed raw data with GIS tools on a supercomputer, and presented findings at the All India ISRO Conference, achieving precise geospatial feature identification.
    }
