\section{Text Formatting}

This section contains various text formatting settings in Latex.

\subsection{Font Styles}

\textbf{This is bold text.}\\
\textit{This is italic text.}\\
\underline{This is underlined text.}\\
\texttt{This is typewriter (monospaced) text.}\\
\textsc{This is small caps text.}\\
\emph{This is emphasized text.}

\subsection{Font Sizes}

\tiny{This is tiny text.}\\
\scriptsize{This is scriptsize text.}\\
\footnotesize{This is footnotesize text.}\\
\small{This is small text.}\\
\normalsize{This is normal size text.}\\
\large{This is large text.}\\
\Large{This is larger text.}\\
\LARGE{This is even larger text.}\\
\huge{This is huge text.}\\
\Huge{This is hugest text.}

\subsection{Text Colors}
\normalsize
\textcolor{red}{This is red text.}\\
\textcolor{blue}{This is blue text.}\\
\textcolor{green}{This is green text.}\\
\textcolor{codehighlight}{This is custom color text.}

\subsection{Combined Formatting}

\textbf{\textit{This is bold and italic text.}}\\
\underline{\textbf{\textit{This is bold, italic, and underlined text.}}}\\
\textcolor{blue}{\textbf{This is bold blue text.}}

\subsection{Bullet Points}
\begin{itemize}
    \item \textbf{Preprocessor Directives}
    \item \textbf{Global Declarations}
    \item \textbf{Function Definitions}
\end{itemize}

\subsection{Notes}
\begin{quote}
    This is a note or block quote in LaTeX.
\end{quote}
\begin{tcolorbox}[colback=yellow!10!white, colframe=yellow!50!black, title=Note]
    This is a customized note or block quote in LaTeX using tcolorbox.
\end{tcolorbox}