% References Section
\section{References}

\begin{enumerate}

% Book example
\item Smith, J. D. (2009). \textit{The Art of Writing}. Random House.
% Edited book example
\item Smith, A. B. (Ed.). (2010). \textit{Advances in Linguistics}. Cambridge University Press.
% Journal article example (print)
\item Jones, S. C., \& Davis, R. J. (2017). Understanding cultural intelligence. \textit{Journal of Cross-Cultural Psychology, 48}(4), 493-514. \url{https://doi.org/10.1177/0022022117704302}
% Journal article example (online)
\item Roberts, T. F., \& Hidajat, M. (2020). Exploring the impact of social media on adolescent development. \textit{Journal of Adolescent Research, 35}(2), 187-210. \url{https://doi.org/10.1177/0743558420913356}
% Website example with author
\item Davis, M. (2018). Understanding climate change. Retrieved from \url{https://www.example.com/climate-change}
% Website example without author
\item National Institute of Mental Health. (2021). Depression in children and teens. Retrieved from \url{https://www.nimh.nih.gov/health/topics/depression}
% Chapter in edited book example
\item Green, R. T. (2012). Language development in early childhood. In P. H. Smith (Ed.), \textit{Language Acquisition: Theoretical Approaches} (pp. 45-68). Oxford University Press.
% Newspaper article example
\item Smith, J. (2022, June 15). New trends in technology. \textit{The New York Times}, pp. A1, A10.
% Report or government document example
\item United Nations. (2015). \textit{Sustainable Development Goals: 17 Goals to Transform Our World}. Author.
% Conference paper example
\item Brown, L. M. (2019). Education reform in the digital age. Paper presented at the Annual Conference of the American Educational Research Association, Toronto, Canada.
% Thesis or dissertation example
\item Johnson, S. L. (2018). \textit{Understanding leadership in nonprofit organizations} (Doctoral dissertation). Harvard University.

\end{enumerate}

